---
output: 
  github_document:
    df_print: kable
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ncaavolleyballr

```{r echo=FALSE}
library(ncaavolleyballr)
```

<!-- badges: start -->
[![Project Status: WIP - Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![Codecov test coverage](https://codecov.io/gh/JeffreyRStevens/ncaavolleyballr/graph/badge.svg)](https://app.codecov.io/gh/JeffreyRStevens/ncaavolleyballr)
<!-- badges: end -->

Inspired by the NCAA data extraction functions from the [`{baseballr}`](https://billpetti.github.io/baseballr/) package, the goal of `{ncaavolleyballr}` is to extract women\'s and men\'s volleyball information from the NCAA website. The functions in this package can extract team records/schedules and player statistics for the 2020-`r ncaavolleyballr:::most_recent_season()` NCAA women\'s and men\'s divisions I, II, and III volleyball teams. Functions can aggregate statistics for teams, conferences, divisions, or custom groups of teams.

## Installation

You can install developmental versions from [GitHub](https://github.com/) with:

```{r eval = FALSE}
# install.packages("remotes")
remotes::install_github("JeffreyRStevens/ncaavolleyballr")
```

## Usage

```{r eval=FALSE}
library(ncaavolleyballr)
```


The NCAA uses a unique team ID for each women\'s and men\'s volleyball team and each season. So first you will need to get that ID with the `find_team_id()`. For instance, to find the ID for University of Nebraska\'s 2024 season:
```{r}
find_team_id("Nebraska", 2024)
```

With this team ID, you can now extract team information about the arena, coach, record, and schedule with `team_season_stats()`.

```{r}
team_info <- find_team_id("Nebraska", 2024) |> 
  team_season_stats()
team_info$arena
team_info$coach
team_info$record
team_info$schedule
```

There is also roster and overall season performance data on individual players with the `team_player_stats()`. 

```{r}
find_team_id("Nebraska", 2024) |> 
  team_player_stats()
```

By default, these functions return information on women\'s teams, but they can be set to return men\'s information.

```{r}
find_team_id("UCLA", 2023, sport = "MVB") |> 
  team_player_stats()
```


## Citation

To cite `{ncaavolleyballr}`, use:

> Stevens, Jeffrey R. (2025). ncaavolleyballr: Extract data from NCAA women\'s volleyball website.
> (version 0.1.0)
> <https://github.com/JeffreyRStevens/ncaavolleyballr>


