---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# volleyballr

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The goal of `{volleyballr}` is to extract women's and men's volleyball information from the NCAA website.

## Installation

You can install developmental versions from [GitHub](https://github.com/) with:

```{r eval = FALSE}
# install.packages("remotes")
remotes::install_github("JeffreyRStevens/volleyballr")
```

## Usage

```{r}
library(volleyballr)
```


The NCAA uses a unique team ID for each women's and men's volleyball team and each season. So first you will need to get that ID with the `find_team_id()`. For instance, to find the ID for University of Nebraska's 2024 season:
```{r}
find_team_id("Nebraska", 2024)
```

With this team ID, you can now extract team information about the arena, coach, record, and schedule.

```{r}
team_info <- find_team_id("Nebraska", 2024) |> 
  team_season_stats()
team_info$arena
team_info$coach
team_info$record
team_info$schedule
```

There is also roster and overall season performance data on individual players. 

```{r}
find_team_id("Nebraska", 2024) |> 
  team_player_stats() |> 
  knitr::kable()
```

By default, these functions return information on women's teams, but they can be set to return men's information.

```{r}
find_team_id("UCLA", 2023, sport = "MVB") |> 
  team_player_stats() |> 
  knitr::kable()
```


## Citation

To cite `{volleyballr}`, use:

> Stevens, Jeffrey R. (2024). volleyballr: Extract data from NCAA women's volleyball website.
> (version 0.1.0)
> <https://github.com/JeffreyRStevens/volleyballr>


